% Preface -----------------------------------------------------------------------------------------
\chapter*{Preface}

This Master's thesis presents the development and implementation of a robot-based methodology for the characterization of Single-Use Bag Mixers. The aim of this research is to advance the precision and efficiency of mixing performance assessments within bioprocess engineering.

The project addresses critical challenges in the industry, including the necessity for precise and reproducible evaluations of mixer performance and the integration of automated systems in laboratory environments. The developed robotic method not only improves the accuracy of these assessments but also significantly enhances the efficiency by reducing the time and manual effort required.

This research has been conducted under the supervision of Prof. Dr.-Ing. Stephan Behr, whose expert guidance and insights were invaluable throughout the course of this project. I am also deeply grateful to Marius Kling, M.Sc., for his technical support and constructive feedback.

I would like to acknowledge the support and collaboration of [Company/Institution Name], whose resources and partnership were instrumental to the success of this project.

The findings and methodologies presented in this thesis contribute to the advancement of bioprocessing technologies, providing a robust foundation for future research and development in the field.

Leverkusen, \today

\addcontentsline{toc}{chapter}{Preface}
